\pkg{RProtoBuf}: Efficient Cross-Language Data Serialization in R

### 2014-01-12 papers/jss/article.Rnw
tiny changes for that my IDE needs
git-svn-id: svn://svn.r-forge.r-project.org/svnroot/rprotobuf@754 edb9625f-4e0d-4859-8d74-9fd3b1da38cb
move a strayed sentence
git-svn-id: svn://svn.r-forge.r-project.org/svnroot/rprotobuf@755 edb9625f-4e0d-4859-8d74-9fd3b1da38cb
rewrite paragraph
git-svn-id: svn://svn.r-forge.r-project.org/svnroot/rprotobuf@757 edb9625f-4e0d-4859-8d74-9fd3b1da38cb

\begin{document}

@@

Once the data serialization needs of an application become complex
enough, developers typically benefit from the use of an
\emph{interface description language}, or \emph{IDL}.  IDLs like
Protocol Buffers \citep{protobuf}, Apache Thrift, and Apache Avro provide a compact
well-documented schema for cross-langauge data structures and
efficient binary interchange formats.  The schema can be used to
generate model classes for statically-typed programming languages such
as C++ and Java, or can be used with reflection for dynamically-typed
programming languages.  Since the schema is provided separately from
the encoded data, the data can be efficiently encoded to minimize
storage costs of the stored data when compared with simple
``schema-less'' binary interchange formats.

@@

Many sources compare data serialization formats and show Protocol
Buffers very favorably to the alternatives; see
\citet{Sumaray:2012:CDS:2184751.2184810} for one such comparison.

@@

Before one can create a new Protocol Buffer Message or parse a
serialized stream of bytes as a Message, one must first read in the message
type specification from a \texttt{.proto} file.

New \texttt{.proto} files are imported with the \code{readProtoFiles}
function, which can import a single file, all files in a directory, or
all \texttt{.proto} files provided by another R package.

The \texttt{.proto} file syntax for defining the structure of protocol
buffer data is described comprehensively on Google Code\footnote{See 
\url{http://code.google.com/apis/protocolbuffers/docs/proto.html}.}.

Once the proto files are imported, all message descriptors are
are available in the R search path in the \texttt{RProtoBuf:DescriptorPool}
special environment. The underlying mechanism used here is
described in more detail in Section~\ref{sec-lookup}.

>>>>

\begin{document}
\SweaveOpts{concordance=FALSE}

@@

Once the data serialization needs of an application become complex
enough, developers typically benefit from the use of an
\emph{interface description language}, or \emph{IDL}.  IDLs like
Protocol Buffers \citep{protobuf}, Apache Thrift, and Apache Avro provide a compact
well-documented schema for cross-langauge data structures and
efficient binary interchange formats.  The schema can be used to
generate model classes for statically-typed programming languages such
as C++ and Java, or can be used with reflection for dynamically-typed
programming languages.  Since the schema is provided separately from
the encoded data, the data can be efficiently encoded to minimize
storage costs of the stored data when compared with simple
``schema-less'' binary interchange formats.
Many sources compare data serialization formats and show Protocol
Buffers very favorably to the alternatives; see
\citet{Sumaray:2012:CDS:2184751.2184810} for one such comparison.

@@

@@

To create or parse a Protocol Buffer Message, one must first read in 
the message type specification from a \texttt{.proto} file. The 
\texttt{.proto} files are imported using the \code{readProtoFiles}
function, which can either import a single file, all files in a directory,
or every \texttt{.proto} file provided by a particular R package.
The \texttt{.proto} file syntax for defining the structure of protocol
buffer data is described comprehensively on Google Code\footnote{See 
\url{http://code.google.com/apis/protocolbuffers/docs/proto.html}.}.

After importing proto files, the corresponding message descriptors are
available from the \texttt{RProtoBuf:DescriptorPool} environment in 
the R search path. The underlying mechanism used here is
described in more detail in Section~\ref{sec-lookup}.

%JO: can we just move the section 7 to here? It's only one paragraph%
